\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

% MARGINS
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\titleformat{\section}{\scshape\raggedright\large\bfseries}{}{0em}{}[\titlerule]

\pdfgentounicode=1
\raggedright
\raggedbottom
\setlist[itemize]{noitemsep,topsep=2pt,leftmargin=0.15in}

\begin{document}

%--------HEADER--------
    {\LARGE \textbf{AAYUSH ACHARYA}}\\[2pt]
    Liverpool, NSW 2170 \textbullet{} 0448 113 330 \textbullet{} \href{mailto:aayushh@outlook.com.au}{aayushh@outlook.com.au} \\
    \href{https://linkedin.com/in/aayushacharya}{linkedin.com/in/aayushacharya} \textbullet{} \href{https://aayushacharya.com.au}{aayushacharya.com.au}

%--------SUMMARY--------
\section{Summary}
IT Support Officer (Level 1/2) with hands-on experience supporting 200+ end users across multi-site environments. Skilled in troubleshooting Microsoft 365, Active Directory, hardware, and network issues with a strong focus on fast resolution and user satisfaction. Proven ability to handle high ticket volumes, resolve issues at first contact, and support business-critical systems in fast-paced environments.

\textbf{Key Skills:} Active Directory, Password Resets, Microsoft 365 Support, Hardware Troubleshooting, Ticketing Systems, Remote Support, User Onboarding/Offboarding, Networking Basics

%--------EXPERIENCE--------
\section{Professional Experience}

\textbf{IT Support Officer} \hfill Jul 2024 -- Present \\
Al Aseel Group, Sydney, NSW
\begin{itemize}
  \item Provide Level 1/2 IT support to 200+ users across 9 locations via phone, email, and in-person support.
  \item Handle 25–40 support requests daily, resolving ~95\% of issues at first contact
    \item Supported Microsoft 365 services including Exchange, Teams, and SharePoint.
  \item Troubleshoot Microsoft 365 issues including Outlook, Teams, OneDrive, and user access problems.
  \item Manage Active Directory and Entra ID accounts including password resets, account lockouts, onboarding, and offboarding.
  \item Support POS systems (Lightspeed), iPads, and payment terminals, ensuring minimal downtime during service hours.
  \item Troubleshoot hardware issues including printers, desktops, laptops, and network connectivity (DNS/DHCP/Wi-Fi).
  \item Assist with VoIP (3CX) user setup and basic telephony troubleshooting.
  \item Create and manage user accounts, shared mailboxes, and distribution lists in Microsoft 365.
\item Monitor and respond to system alerts and outages, ensuring minimal disruption to business operations.
\item Document recurring issues and resolutions to improve internal knowledge base and reduce repeat tickets.
\item Configure and deploy new devices including laptops, mobile devices, and POS hardware for new staff.
\item Support network infrastructure including routers, switches, and Wi-Fi access points across multiple sites.
\item Assist in implementing security best practices such as MFA setup and endpoint protection.
\item Collaborate with vendors and third-party providers to resolve escalated technical issues.
\end{itemize}

\vspace{6pt}

\textbf{IT Support Analyst (Level 1/2) – Internship} \hfill 2023 -- 2024 \\
909IT Solutions, Parramatta, NSW
\begin{itemize}
  \item Resolved Level 1/2 support tickets using Jira, supporting users via phone and email.
  \item Performed password resets, account unlocks, and user account management in Active Directory.
    \item Use remote support tools to assist users across multiple locations.
  \item Maintain system uptime and support business-critical operations in a high-pressure environment.
  \item Installed and configured Windows OS, software, and devices for end users.
  \item Troubleshot hardware, network, and software issues across client environments.
  \item Escalated complex issues to senior engineers while ensuring proper documentation.
\end{itemize}

\vspace{6pt}

\textbf{Customer Service \& Leadership Roles} \\
Al Aseel Group, Sydney, NSW \\
Venue Operations Manager(2022--2024) | Assistant Restaurant Manager (2020--2022) | Food \& Beverage Supervisor (2020--2021) 
 \begin{itemize} \item Led diverse teams of 15+ staff in high-pressure environments, managing rostering, staff training, and conflict resolution across multiple high-volume venues. 
 \item Acted as the first point of contact for basic IT issues on shift, resolving login, POS, and connectivity problems without escalation.
\item Trained staff on POS systems, online booking platforms, and internal tools, reducing user errors and support requests.
\item Coordinated with IT support teams to report system issues, provide detailed troubleshooting information, and ensure timely resolution.
\item Supported onboarding of new staff by setting up system access and guiding them through software and device usage.
\item Identified recurring technical issues during service and communicated patterns to IT teams to support long-term fixes.
\item Maintained smooth business operations by quickly adapting to system failures and implementing temporary workarounds.
 \end{itemize}

\newpage

%--------CORE TECHNICAL SKILLS--------
\section{Core Technical Skills}
\begin{minipage}[t]{0.48\textwidth}
\begin{itemize}
  \item \textbf{Service Desk:} Level 1/2 support, SLA management, ticketing
  \item \textbf{Identity \& Access:} Entra ID (Azure AD), AD, RBAC, MFA
  \item \textbf{M365:} Exchange, Teams, OneDrive, SharePoint
  \item \textbf{Security:} Conditional Access, VPN, Phishing-Resistant MFA
  \item \textbf{Endpoint Mgmt:} Intune, Autopilot, Jamf
\end{itemize}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\begin{itemize}
  \item \textbf{ITSM:} Servicenow, Freshservice
  \item \textbf{Networking:} DNS, DHCP, TCP/IP, Cisco Meraki
  \item \textbf{Cloud:} Microsoft Azure, hybrid cloud infrastructure
  \item \textbf{Infrastructure:} Hyper V, Windows Server 2022, GPO
  \item \textbf{Hardware:} Laptops, POS terminals, AV, VoIP (3CX)
  \item \textbf{SaaS Apps:} Lightspeed, Deputy, Monday.com
    \item \textbf{Remote Support:} AnyDesk, remote troubleshooting

\end{itemize}
\end{minipage}
%----------CERTIFICATIONS----------
\section{Certifications \& Training}
\begin{itemize}
  \item \textbf{Microsoft Cloud Support Associate} -- Microsoft / Coursera 
  \item \textbf{MD-102: Endpoint Administrator} -- Packt / Coursera 
  \item \textbf{Cisco CCST IT Support (100-140)} -- Pearson / Coursera 
  \item \textbf{Google IT Support Professional Certificate} -- Google / Coursera 
  \item \textbf{CompTIA A+ Core 1 Preparation} -- Pearson / Coursera 
\end{itemize}
\textit{Full credentials portfolio: \href{https://aayushacharya.com.au/certifications.pdf}{aayushacharya.com.au/certifications.pdf}}
%--------EDUCATION--------
\section{Education}
\textbf{Bachelor of Computer Applications (Cloud \& Security)} \\
\textit{Manipal University}
\vspace{2pt}
\begin{itemize}
  \item \textbf{Academic Focus:} Cyber Security, Hybrid Cloud Infrastructure, Enterprise Network Administration, Software/Web Development.
  \item \textbf{Relevant Coursework:} Enterprise Cloud Computing, Network Security Fundamentals, Linux System Administration, Database Management Systems (DBMS).
\end{itemize}

\vspace{5pt}

\textbf{Bachelor of Information Technology (Undergraduate Coursework)} $|$ 2018 -- 2020 \\
\textit{King's Own Institute (KOI), Sydney}
\begin{itemize}
  \item Completed 2 years of core coursework building a foundational understanding of Information Technology and network architecture.
\end{itemize}

%--------TECHNICAL PROJECTS--------
\section{Technical Projects | Home Lab}
\textbf{Enterprise Infrastructure \& Security Architecture (Microsoft 365 E5)}
\begin{itemize}
  \item \textbf{Identity \& Access Management (IAM):} Architected a production-grade Microsoft 365 E5 tenant, implementing Entra ID (Azure AD) to manage user lifecycles and enforce strict Role-Based Access Control (RBAC) across the simulated enterprise.
  \item \textbf{Zero Trust Security Framework:} Engineered granular Conditional Access policies and enforced Phishing-Resistant MFA, reducing the theoretical attack surface by restricting access based on user risk and device compliance signals.
  \item \textbf{Endpoint Management Strategy:} Orchestrated MDM workflows using Microsoft Intune, configuring Windows Autopilot profiles for zero-touch device provisioning and automated patch compliance.
  \item \textbf{Hybrid Infrastructure Simulation:} Deployed virtualised Windows Server 2022 instances to simulate on-premise infrastructure, hardening security posture through advanced GPO configurations and network segmentation.
  \item \textbf{DNS \& Network Architecture:} Administered complex public DNS zones, configuring MX and TXT records to authenticate enterprise email servers and utilising A/CNAME records for custom domain redirection.
\end{itemize}
%----------ADDITIONAL INFORMATION----------
\section{Additional Details}
\begin{itemize}
  \item \textbf{Continuous Learning:} Actively pursuing CCNA and Microsoft Azure certifications to deepen network security and cloud infrastructure capability alongside daily service desk operations.
  \item \textbf{Mobility:} Full NSW Driver's Licence with own vehicle; available for on-site support across Greater Sydney.
  \item \textbf{Work Rights:} Full Australian working rights; available for rotating roster shifts.
\end{itemize}

\end{document}
